Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-22 latex/main.tex
Updates from Overleaf

\begin{figure}
\centering
% NOTE the size of the second "m" column doesn't matter, but we have to fix the
% size in order for vertical centering to work :sigh:
% The layout here isn't ideal, but it's incredibly fiddly to get center
% alignment veritically with cells to work, so this is good enough.
\begin{tabularx}{0.85\textwidth}{>{\centering\arraybackslash}m{1cm}>{\arraybackslash}m{1cm}}
Q1 & \includegraphics[height=\cprheight]{static/RE_node-QCpass-427863.png}\\
Q2 & \includegraphics[height=\cprheight]{static/RE_node-QCfail-748991.png}\\
Q3 & \includegraphics[height=\cprheight]{static/RE_node-QCfail-411345.png}\\
Q4 & \includegraphics[height=\cprheight]{static/RE_node-QCfail-663484.png}\\
\end{tabularx}
\caption{
Illustrative copying patterns
drawn from the quadrants labeled in Figure~\ref{fig:recombinant_qc}. Q1-Q4 correspond to copying patterns for recombination nodes 427863, 728991, 411345, and 663484 (none of which are associated with designated Pango recombinant lineages).
The SnpIt-like~\cite{OToole2024} schematic highlights the set of genomic positions
where the allelic state in a recombinant
(middle row, labelled by node ID)
matches that of the suggested left (P0, above, coloured green) or right parent (P1, below, coloured blue),
or where the recombination event requires a de-novo mutation (gold).
Genomic positions are shown above each column, with the allelic state of the Wuhan-Hu-1 reference genome (``ref'') immediately below;  parental states that are not inherited by the recombinant and correspond to the reference are shown with a grey background.
At the Adjacent genomic positions are underlined in red, and
near-adjacent sites (within 3 bases) in orange.
A continuous red+orange underline thus indicates
a region treated as a single locus.
For further context, mutations above a recombination event
are shown on the bottom.
}
\label{fig:copying_pattern_examples}
\end{figure}

>>>>

\begin{figure}
\centering
% NOTE the size of the second "m" column doesn't matter, but we have to fix the
% size in order for vertical centering to work :sigh:
% The layout here isn't ideal, but it's incredibly fiddly to get center
% alignment veritically with cells to work, so this is good enough.
\begin{tabularx}{0.85\textwidth}{>{\centering\arraybackslash}m{1cm}>{\arraybackslash}m{1cm}}
Q1 & \includegraphics[height=\cprheight]{static/RE_node-QCpass-427863.png}\\
Q2 & \includegraphics[height=\cprheight]{static/RE_node-QCfail-748991.png}\\
Q3 & \includegraphics[height=\cprheight]{static/RE_node-QCfail-411345.png}\\
Q4 & \includegraphics[height=\cprheight]{static/RE_node-QCfail-663484.png}\\
\end{tabularx}
\caption{
Illustrative copying patterns
drawn from the quadrants labeled in Figure~\ref{fig:recombinant_qc}. Q1-Q4 correspond to copying patterns for recombination nodes 427863, 728991, 411345, and 663484, none of which are associated with designated Pango recombinant lineages.
The SnpIt-like~\cite{OToole2024} schematic highlights the specific genomic positions
where the allelic state in a recombinant
(middle row, labelled by node ID)
matches that of the suggested left (P0: upper row, coloured green) or right parent (P1: lower row, coloured blue),
or where the recombination event requires a de-novo mutation (gold, with mutational change at bottom).
Genome position (``pos'') is shown above each column, with the allelic state of the Wuhan-Hu-1 reference genome (``ref'') immediately below;  parental states that correspond to the reference but are not inherited by the recombinant are shown with a gray background.
Underneath each copying pattern, adjacent genomic positions are underlined in red, and
near-adjacent sites (within 3 bases) in orange.
A continuous red-and-orange underline thus indicates
a region treated as a single ``locus'' for the purposes of quality control (see Supplementary S1.XXX).
}
\label{fig:copying_pattern_examples}
\end{figure}
